\section{Gotchas, Futures}
\index{Gotchas}
\index{Futures}

Here we layout all the unimplemented features and current known bugs for versions 6.0 through 6.6 Releases of the firmware

\begin{description}

\item [Web Site] use http://community.webbricksystems.com/ for all WebBrick news.

\item [Split Scene Banks]

	On first power up, buttons that do a 'Next' from scene 8 onwards will actually do a next from scene 0
	until scene 8 is selected.  The simple workaround is to press any 'off' buttons just after WebBrick power up.

    This has been fixed in WebBrick firmware 6.6 onwards. 

\item[Analogue 0utputs Version 6.1 onwards]

From version 6.1 of the WebBrick we have included a diode to protect against reverse polarity at the supply rails. 
This effectively drops the internal 12v supply rail by 0.6V.  This means that for WebBricks that are supplied with 
12.0V or less, the top end of the analogue output drops to about 9.67V.  The simple solution is to ensure that the 
WebBrick are supplied with a little more than 12V.  12.6-18.0V is fine.  Note that 13.6-13.8V power supplies are 
particularly suitable for float charging sealed lead acid batteries.

\item[Configuring Digital Inputs]

In version 6.1 it is possible to configure things like a high threshold for a digital channel. 
This is a meaningless configuration. It does no harm, but conversely does nothing at all.

\item[udp Types]

  From 6.6 onwards there is only one UDP type for Digital Inputs, the 'Remote' and 'Alarm' types have been removed.


\end{description}
