\section{Revision}
\index{Revision}

This section highlights changes to WebBricks and WebBrick firmware.

\subsection{6.3}

\begin{enumerate}
\item
Added Real Time clock support.
\item
All 12 digital inputs can support rotary encoders. Connecting rotary encoder to dedicated terminals no longer supported.
\end{enumerate}

\subsection{6.4}

\begin{enumerate}
\item
Added hardware and command to switch mimic output from 4V to 10V, this enables using some more generic switches that are designed for 
higher voltages.

\item
Added hardware to suppoprt RS232 and RS485 serial interfaces, only one of which can be active at any time.

\item
Added minimal support in firmware to configure the serial interface and access it from the Gateway over http.

\item
Added support in firmware to use the serial port for DMX control.

\item
Add Dwell On and Dwell off commands. This extends the dwell options. Dwell Always will always dwell the output, Dwell On only actions the dwell 
if the output is currently off, dwell off starts a dwell timer to switch an output off if it is currently on and dwell cancel switches an output
off if currently on or switches it on for dwell time if off.

\end{enumerate}
\subsection{7.0}

\begin{enumerate}
\item
Changed connections for Relay 4 so that all connections go to 'Relay 4B'.

\item
Introduced dual power supplies so that noise or shorts on the temperature sensor bus do not compromise the operation of the WebBrick.

\item
Changed the watchdog scheme so that the web server is power cycled on network disruption.

\item Upgraded the open collector outputs to handle 3 Amps.


\end{enumerate}
